An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2022-02-20 article/latex_files/ch3/3-0-design-principles.tex
final modifications

For designing an extendable implementation of ROMC, we firstly define
ROMC as a sequence of algorithmic steps. The algorithmic view of ROMC
serves as the driver for the implementation at \pkg{ELFI}. At a high
level, ROMC can be split into the training and the inference part. In
general terms, the training part covers all steps for estimating the
proposal regions and the inference part calculates the weighted
samples. Algorithm~\ref{alg:romc_algorithm} defines ROMC formally;
Steps 2-10 (before the horizontal line) form the training part and
steps 12-17 the inference part, respectively.

\begin{algorithm}[!ht]
	\caption{ROMC. Requires the prior \( p(\thetab) \), the simulator
    \(M_r(\thetab)\), number of optimisation problems \(n_1\), number
    of samples per region \(n_2\), acceptance limit
    \(\epsilon\)}\label{alg:romc_algorithm}
	\begin{algorithmic}[1]
    \Procedure{ROMC}{}
    \For{\(i \gets 1 \textrm{ to } n_1\)}
    \State \(\vb_i \sim p(\vb)\) \Comment{Draw nuisance variables}
    \State Convert \(M_r(\thetab) \) to \( g(\thetab, \vb=\vb_i) \) \Comment{Define deterministic simulator}
      \State \( d_i(\thetab) = ||g(\thetab, \vb=\vb_i) - \yb_0||_2 \) \Comment{Define distance function}
      \State \(\thetab_i^* = \text{argmin}_{\thetab} d_i\), \(d_i^*=d_i(\thetab_i^*)\) \Comment{Solve optimisation problem}
      \If{\(d^*_i > \epsilon\)}
        \State Go to 2 \Comment{Filter solution}
      \EndIf
      \State Estimate \(\mathcal{\hat{S}}_i\) and define \(q_i\) \Comment{Estimate proposal area}
      \State (Optional) Fit \(\Tilde{d}_i\) on \(\mathcal{\hat{S}}_i\) \Comment{Fit surrogate model}
      \\\hrulefill
      \For{\(j \gets 1 \textrm{ to } n_2\)}
      \State \(\thetab_{ij} \sim q_i\), compute \(w_{ij}\) as in Algorithm \ref{alg:sampling_GB} \Comment{Sample}
      \EndFor
    \EndFor
    \State \(\E_{p(\thetab|\data)}[h(\thetab)]\) as in eq.~\eqref{eq:expectation} \Comment{Estimate an expectation}
    \State \(p_{d,\epsilon}(\thetab) \) as in eq.~\eqref{eq:approx_posterior_omc} \Comment{Evaluate the unnormalised posterior}
    \EndProcedure
	\end{algorithmic}
\end{algorithm}

\subsubsection*{Training part}
\noindent
At the training (fitting) part, the goal is the estimation of the
proposal regions \(\mathcal{\hat{S}}_i\). The tasks are; (a) sampling
the nuisance variables \(\vb_i \sim p(\vb)\) for obtaining the
deterministic functions \(d_i(\thetab)\), (b) defining the optimisation
problems \(\min_{\thetab} \: d_i(\thetab)\), (c) obtaining
\(\thetab_i^*\), \(d_i^*\) (d) checking whether \(d_i^* \leq \epsilon\) and
(e) computing the proposal distribution \(q_i\).

If \(d_i(\thetab)\) is differentiable, using a gradient-based method
is advised for obtaining \(\thetab_i^*\) faster. In this case, the
gradients \(\nabla_{\thetab} d_i\) gradients are approximated
automatically with finite-differences. This approximation requires two
evaluations of \(d_i\) for \emph{each} parameter
\(\theta_d, d \in \{1, \ldots, D\}\)\footnote{\(D\) is the
  dimensionality of \(\thetab\), i.e.  \(\thetab \in \mathbb{R}^D\)},
which works in low-dimensional problems. If \(d_i(\thetab)\) is not
differentiable, Bayesian Optimisation can be used as an alternative
solution. In this scenario, the training part becomes slower due to
fitting of the surrogate model and the blind optimisation steps.

After obtaining the optimal points \(\thetab^*\), we estimate the
proposal regions. Algorithm~\ref{alg:region_construction} describes
the line search approach for finding the region's boundaries. An
important step for the proposal region estimation is deciding the axes
of the bounding box; the directions \(\vb_d, d = \{1, \ldots, D\}\) we
follow for reaching the boundaries. We approximate them as the
direction of the highest curvature of \(d_i\) at \(\thetab_i^*\). This
estimation is given by the eigenvalues of the Hessian matrix
\(\hessian_i\) of \(d_i\)\footnote{Either the real distance \(d_i\) or
  the Gaussian Process approximation \(\hat{d}_i\)} at
\(\thetab_i\). The Hessian matrix is approximated numerically. In case
where the distance function is the Euclidean, the Hessian matrix can
be also computed as \(\hessian_i = \jac_i^T\jac_i\), where \(\jac_i\)
is the Jacobian matrix of the summary statistics
\(\Phi(g(\thetab, \vb=\vb_i))\) at \(\thetab_i^*\). The approximation
through the Jacobian matrix has the computational advantage of using
only first-order derivatives.

@@

\begin{algorithm}[!ht]
	\caption{Approximation of \(\mathcal{\hat{S}}_i\) with a bounding box; 
  Requires: a model of distance \(d_i(\thetab)\), 
  an optimal point \(\thetab_i^*\), 
  a number of refinements \(K\), 
  a step size \(\eta\_\text{start}\), 
  maximum iterations \(M\) and 
  a curvature matrix \(\hessian_i\) (\(\jac_i^T\jac_i \) or GP Hessian)}\label{alg:region_construction}
	\begin{algorithmic}[1]
	\State Compute eigenvectors \(\vb_{d}\) of \(\hess_i\) {\scriptsize (\(d = 1,\ldots,||\thetab ||)\)}
	\For{\(d \gets 1 \textrm{ to } D\)}
		\State \(\Tilde{\thetab} \gets \thetab_i^*\) \label{algstep:box_constr_start}
		\State \(k \gets 0\)
		\State \(\eta \gets \eta\_\text{start}\) \Comment{Initialize \(\eta\)}
		\Repeat
          \State \(j \gets 0\)
        	\Repeat
            \State \(\Tilde{\thetab} \gets \Tilde{\thetab} + \eta \ \vb_{d}\) \Comment{Large step size \(\eta\).}
            \State \(j \gets j + 1\)
        	\Until{\(d(f_i(\Tilde{\thetab}), \data) > \epsilon\) or \(j \geq M\)} \Comment{Check distance or maximum iterations}
        	\State \(\Tilde{\thetab} \gets \Tilde{\thetab} - \eta \ \vb_{d}\)
        	\State \(\eta \gets \eta/2\) \Comment{More accurate region boundary}
        	\State \(k \gets k + 1\)
      \Until \(k = K\)
      \If{\(\Tilde{\thetab} = \thetab_i^*\)} \Comment{Check if no step has been done}
        \State \(\Tilde{\thetab} \gets \Tilde{\thetab} + \dfrac{\eta\_{\text{start}}}{2^K} \vb_d\) \Comment{Then, make the minimum step}
      \EndIf \label{algstep:box_constr_end}
    	\State Set \(\Tilde{\thetab}\) as the positive end point along \(\mathbf{v}_{d}\)
    	\State Runc steps~\ref{algstep:box_constr_start}~-~\ref{algstep:box_constr_end} for \(\mathbf{v}_{d} = - \mathbf{v}_{d}\) and set \(\Tilde{\thetab}\) as the negative end point along \(\mathbf{v}_{d}\)
	\EndFor
	\State Fit a rectangular box around the region end points and define \(q_i\) as uniform distribution
	\end{algorithmic}
\end{algorithm}

>>>>

For designing an extendable implementation, we firstly define ROMC as
a sequence of algorithmic steps, which is the driver for the
implementation that follows. At a high level, ROMC can be split into
the training and the inference part. In broad view, the training part
covers all steps for estimating the proposal regions and the inference
part calculates the weighted
samples. Algorithm~\ref{alg:romc_algorithm} defines ROMC formally;
Steps 2-11 (before the horizontal line) form the training part and
steps 13-18 the inference part.

\begin{algorithm}[!ht]
	\caption{ROMC. Requires the prior \( p(\thetab) \), the simulator
    \(M_r(\thetab)\), number of optimisation problems \(n_1\), number
    of samples per region \(n_2\), acceptance limit
    \(\epsilon\)}\label{alg:romc_algorithm}
	\begin{algorithmic}[1]
    \Procedure{ROMC}{}
    \For{\(i \gets 1 \textrm{ to } n_1\)}
    \State \(\ub_i \sim p(\ub)\) \Comment{Draw nuisance variables}
    \State Convert \(M_r(\thetab) \) to \( g(\thetab, \ub=\ub_i) \) \Comment{Define deterministic simulator}
      \State \( d_i(\thetab) = d(g(\thetab, \ub=\ub_i), \yb_0) \) \Comment{Define distance function}
      \State \(\thetab_i^* = \text{argmin}_{\thetab} d_i\), \(d_i^*=d_i(\thetab_i^*)\) \Comment{Solve optimisation problem}
      \If{\(d^*_i > \epsilon\)}
        \State Go to 2 \Comment{Filter solution}
      \EndIf
      \State Estimate \(\hat{\accregioni}\) and define \(q_i\) \Comment{Estimate proposal area}
      \State (Optional) Fit \(\Tilde{d}_i\) on \(\hat{\accregioni}\) \Comment{Fit surrogate model}
      \\\hrulefill
      \For{\(j \gets 1 \textrm{ to } n_2\)}
      \State \(\thetab_{ij} \sim q_i\), compute \(w_{ij}\) as in Algorithm \ref{alg:sampling_GB} \Comment{Sample}
      \EndFor
    \EndFor
    \State \(\E_{p(\thetab|\data)}[h(\thetab)]\) as in eq.~\eqref{eq:expectation} \Comment{Estimate an expectation}
    \State \(p_{d,\epsilon}(\thetab) \) as in eq.~\eqref{eq:approx_posterior_omc} \Comment{Evaluate the unnormalised posterior}
    \EndProcedure
	\end{algorithmic}
\end{algorithm}

\subsubsection*{Training part}
\noindent
At the training (fitting) part, the goal is the estimation of the
proposal regions \(\hat{\accregioni}\). The tasks are; (a) sampling
the nuisance variables \(\ub_i \sim p(\ub)\) for obtaining the
deterministic functions \(d_i(\thetab)\), (b) solving the optimisation
problems \(\min_{\thetab} \: d_i(\thetab)\) for obtaining
\(\thetab_i^*\), \(d_i^*\), and (c) estimate the proposal distribution
\(q_i\).

If \(d_i(\thetab)\) is differentiable, using a gradient-based method
is advised for obtaining \(\thetab_i^*\) faster. In this case, the
gradients \(\nabla_{\thetab} d_i\) gradients are approximated
automatically with finite-differences. This approximation requires two
evaluations of \(d_i\) for \emph{each} parameter
\(\theta_m, m \in \{1, \ldots, D\}\)\footnote{\(D\) is the
  dimensionality of \(\thetab\), i.e.  \(\thetab \in \mathbb{R}^D\)},
which works in low-dimensional problems. If \(d_i(\thetab)\) is not
differentiable, Bayesian Optimisation can be used as an alternative
solution. In this scenario, the training part becomes slower due to
fitting of the surrogate model and the blind optimisation steps.

After obtaining the optimal points \(\thetab^*\), we estimate the
proposal regions. Algorithm~\ref{alg:region_construction} describes
the line search approach for finding the region's boundaries. An
important step for the proposal region estimation is deciding the axes
of the bounding box; the directions \(\vb_m, m = \{1, \ldots, D\}\) we
follow for reaching the boundaries. We approximate them as the
direction of the highest curvature of \(d_i\) at \(\thetab_i^*\). This
estimation is given by the eigenvalues of the Hessian matrix
\(\hessian_i\) of \(d_i\)\footnote{Either the real distance \(d_i\) or
  the Gaussian Process approximation \(\hat{d}_i\)} at
\(\thetab_i\). The Hessian matrix is approximated numerically. In case
where the distance function is the Euclidean, the Hessian matrix can
be also computed as \(\hessian_i = \jac_i^T\jac_i\), where \(\jac_i\)
is the Jacobian matrix of the summary statistics
\(\Phi(g(\thetab, \ub=\ub_i))\) at \(\thetab_i^*\). The approximation
through the Jacobian matrix has the computational advantage of using
only first-order derivatives.

@@

\begin{algorithm}[!ht]
	\caption{Approximation \(\accregioni\) with a bounding box \(\hat{\accregioni}\); 
  Requires: a model of distance \(d_i(\thetab)\), 
  an optimal point \(\thetab_i^*\), 
  a number of refinements \(K\), 
  a step size \(\eta\_\text{start}\), 
  maximum iterations \(M\) and 
  a curvature matrix \(\hessian_i\) (\(\jac_i^T\jac_i \) or GP Hessian)}\label{alg:region_construction}
	\begin{algorithmic}[1]
	\State Compute eigenvectors \(\vb_{m}\) of \(\hess_i\) {\scriptsize (\(d = 1,\ldots,D)\)}
	\For{\(m \gets 1 \textrm{ to } D\)}
		\State \(\Tilde{\thetab} \gets \thetab_i^*\) \label{algstep:box_constr_start}
		\State \(k \gets 0\)
		\State \(\eta \gets \eta\_\text{start}\) \Comment{Initialize \(\eta\)}
		\Repeat
          \State \(j \gets 0\)
        	\Repeat
            \State \(\Tilde{\thetab} \gets \Tilde{\thetab} + \eta \ \vb_{m}\) \Comment{Large step size \(\eta\).}
            \State \(j \gets j + 1\)
        	\Until{\(d(g(\Tilde{\thetab}, \ub=\ub_i), \data) > \epsilon\) or \(j \geq M\)} \Comment{Check distance or maximum iterations}
        	\State \(\Tilde{\thetab} \gets \Tilde{\thetab} - \eta \ \vb_{m}\)
        	\State \(\eta \gets \eta/2\) \Comment{More accurate region boundary}
        	\State \(k \gets k + 1\)
      \Until \(k = K\)
      \If{\(\Tilde{\thetab} = \thetab_i^*\)} \Comment{Check if no step has been done}
        \State \(\Tilde{\thetab} \gets \Tilde{\thetab} + \dfrac{\eta\_{\text{start}}}{2^K} \ub_m\) \Comment{Then, make the minimum step}
      \EndIf \label{algstep:box_constr_end}
    	\State Set \(\Tilde{\thetab}\) as the positive end point along \(\vb_m\)
    	\State Runc steps~\ref{algstep:box_constr_start}~-~\ref{algstep:box_constr_end} for \(\vb_m = - \vb_m\) and set \(\Tilde{\thetab}\) as the negative end point along \(\mathbf{v}_{m}\)
	\EndFor
	\State Fit a rectangular box around the region end points and define \(q_i\) as uniform distribution
	\end{algorithmic}
\end{algorithm}

### 2022-02-20 article/latex_files/ch3/3-1-implementation-principles.tex
final modifications

The overview of our implementation is illustrated in
Figure~\ref{fig:romc_overview}. Following \proglang{Python}'s naming
principles, the methods starting with an underscore (green rectangles)
represent internal (private) functions, whereas the rest (blue
ellipses) are the methods exposed as the public API. In
Figure~\ref{fig:romc_overview}, it can be easily observed that the
implementation follows Algorithm~\ref{alg:romc_algorithm}. The
training part includes all the steps until the computation of the
proposal regions i.e.~sampling the nuisance variables, defining the
optimisation problems, solving them, constructing the regions and
fitting local surrogate models. The inference part comprises of
evaluating the unnormalised posterior (and the normalised when is
possible), sampling and computing an expectation. We also provide some
utilities for inspecting the training process, such as plotting the
histogram of the final distances or visualising the constructed
bounding boxes. Finally, in the evaluation part, we provide two
methods for evaluating the inference; (a) computing the Effective
Sample Size (ESS) of the samples and (b) measuring the divergence
between the approximate posterior the ground-truth, if the latter is
available.\footnote{Normally, the ground-truth posterior is not
  available; However, this functionality is useful in cases where the
  posterior can be computed numerically or with an alternative method
  (i.e.\ ABC Rejection Sampling), and we would like to measure the
  discrepancy between the two approximations.}

@@

ROMC has the significant advantage of being fully parallelisable. We
exploit this fact by implementing a parallel version of all the major
components of the method; (a) solving the optimisation problems, (b)
constructing bounding box regions, (c) sampling and (d) evaluating the
posterior. We parallelise these processes using the built-in
\proglang{Python} package \pkg{multiprocessing}. The specific package
enables concurrency, using subprocesses instead of threads, for
side-stepping the Global Interpreter (GIL). For activating the
parallel version of the algorithm, the user simpy has to pass the
argument \code{parallelize=True} when instantiating \code{ROMC}.

>>>>

The overview of our implementation is illustrated in
Figure~\ref{fig:romc_overview}. Following \proglang{Python}'s naming
principles, the methods starting with an underscore (green rectangles)
represent internal (private) functions, whereas the rest (blue
rectangles) are the methods exposed as the public API. In
Figure~\ref{fig:romc_overview}, it can be easily observed that the
implementation follows Algorithm~\ref{alg:romc_algorithm}. The
training part includes all the steps until the computation of the
proposal regions i.e.~sampling the nuisance variables, defining the
optimisation problems, solving them, constructing the regions and
fitting local surrogate models. The inference part comprises of
evaluating the unnormalised posterior (and the normalised when is
possible), sampling and computing an expectation. We also provide some
utilities for inspecting the training process, such as plotting the
histogram of the final distances or visualising the constructed
bounding boxes. Finally, in the evaluation part, we provide two
methods for evaluating the inference; (a) computing the Effective
Sample Size (ESS) of the samples and (b) measuring the divergence
between the approximate posterior the ground-truth, if the latter is
available.\footnote{Normally, the ground-truth posterior is not
  available; However, this functionality is useful in cases where the
  posterior can be computed numerically or with an alternative method
  (i.e.\ ABC Rejection Sampling), and we would like to measure the
  discrepancy between the two approximations.}

@@

As discussed, ROMC has the significant advantage of being fully
parallelisable. We exploit this fact by implementing a parallel
version of the major fitting components; (a) solving the optimisation
problems, (b) constructing bounding box regions. We parallelise these
processes using the built-in \proglang{Python} package
\pkg{multiprocessing}. The specific package enables concurrency, using
subprocesses instead of threads, for side-stepping the Global
Interpreter (GIL). For activating the parallel version of the
algorithm, the user simpy has to pass the argument
\code{parallelize=True} when instantiating \code{ROMC}.

### 2022-02-20 article/latex_files/ch4/4-1-training.tex
final modifications

\begin{Code}
------------------------------ python snippet ------------------------------
  # Training (fitting) part
  n1 = 500 # number of optimisation problems
  seed = 21 # seed for solving the optimisation problems
  eps = .75 
  use_bo = False # set to True for switching to Bayesian optimisation

@@

  eps = .75 # threshold for the bounding box based on histogram inspection
  romc.estimate_regions(eps=eps) # build the bounding boxes

>>>>

\begin{Code}
------------------------------ python snippet ------------------------------
  # Training (fitting) part
  n1 = 500 # number of optimisation problems
  seed = 21 # seed for solving the optimisation problems
  use_bo = False # set to True for switching to Bayesian optimisation

@@

  eps = .75 # threshold for the bounding box 
  romc.estimate_regions(eps=eps) # build the bounding boxes

### 2022-02-20 article/latex_files/ch4/4-4-extensibility.tex
final modifications

ROMC can be conceived as a meta-algorithm; it describes a sequence of
steps for approximating the posterior distribution, without
\emph{explicitly} enforcing the methods that solve these steps. Even
though for each step a specific algorithm is proposed
by~\cite{Ikonomov2019}, in general ROMC is functional if a practitioner
thinks of an alternative way of approaching a specific
step. Considering this particularity, we designed the implementation
to support such \emph{extensibility} capability.

We have specified four specific points where a user may intervene with
their custom modules; (a) the gradient-based optimisation, (b) the
Bayesian Optimisation, (c) the proposal region construction and (d)
the surrogate model fitting. These are the four critical parts of the
ROMC procedure, whereas the rest of the code is the backbone of the
algorithm; each of them can be swapped to a different
algorithm with the same functionality than the one we propose, without the rest of the method to
collapse.

The four replaceable parts described above, are solved using the four
methods of the \linebreak \code{OptimisatioProblem} class; (a)
\code{solve_gradients(**kwargs)}, (b) \code{solve_bo(**kwargs)},
\linebreak (c) \code{build_region(**kwargs)}, (d)
\code{fit_local_surrogate(**kwargs)}. Therefore, the user should
create a custom class that inherits the basic
\code{OptimisatioProblem} class and overwrites one or more of the
above four functions with custom ones.

We illustrate that in the
following example; suppose we want to blindly set the proposal region
as a predefined n-dimensional bounding box around the optimal
point. The following snippet illustrates how:

\begin{Code}
---------------------------------- python ----------------------------------
class customOptim(OptimisationProblem):
    def __init__(self, **kwargs):
        super(customOptim, self).__init__(**kwargs)

@@

@@

            # train Neural Network
            mlp = MLPRegressor(hidden_layer_sizes=(10,10), solver='adam')
            model = Pipeline([('linear', mlp)])
            model = model.fit(x, y)
            local_surrogates.append(self.create_local_surrogate(model))

        self.local_surrogates = local_surrogates
        self.state["local_surrogates"] = True

    def create_local_surrogate(self, model):
        def _local_surrogate(th):
            th = np.expand_dims(th, 0)
            return float(model.predict(th))
        return _local_surrogate
----------------------------------------------------------------------------    
\end{Code}

In the same way, the user may replace each of the other three
functionalities. The only restriction that must be respected, concerns
the side-effects each method has at the \code{OptimisatioProblem}
class level. In the following four snippets we present the signature
of each method, pointing out with a left arrow the side-effects that
must be included in the custom routine that will replace them.

\begin{Code}
---------------------------------- python ----------------------------------
def solve_gradients(self, **kwargs):
  self.state["attempted"] = True

  # custom solution procedure

  if success:
    self.result = RomcOpimisationResult(res.x, res.y, jac, hess_inv)
    self.state["solved"] = True
    return True 
  else:
    return False 
----------------------------------------------------------------------------    
def solve_bo(self, **kwargs):
  self.state["attempted"] = True

  # custom procedure

  if success:
    self.result = RomcOpimisationResult(x, y)
    self.surrogate <- Callable
    self.state["solved"] = True
    self.state["has_fit_surrogate"] = True
    return True
  else:
    return False
----------------------------------------------------------------------------    
def build_region(self, **kwargs):
    self.eps_region = eps_region

    if success:
        # construct region
        self.regions <- List[NDimBoudningBox]
        self.state["region"] = True
        return True
    else:
        return False
----------------------------------------------------------------------------    
def fit_local_surrogate(self, **kwargs):
  if success:
    self.local_surrogate = local_surrogates
    self.state["local_surrogates"] = True
    return True
  else:
    return False
----------------------------------------------------------------------------    
\end{Code}

>>>>

ROMC describes a sequence of steps for approximating the posterior
distribution, without explicitly enforcing the methods that solve
these steps. Even though for each step a specific algorithm is
proposed by~\cite{Ikonomov2019}, in general ROMC is functional if a
practitioner thinks of an alternative way of approaching a specific
step. Considering this particularity, we designed the implementation
to support extensibility.

We have specified four specific points where a user may intervene with
their custom modules; (a) the gradient-based optimisation, (b) the
Bayesian Optimisation, (c) the proposal region construction and (d)
the surrogate model fitting. These are the four critical parts of the
ROMC procedure, whereas the rest of the code is the backbone of the
algorithm.

The four replaceable parts described above, are solved using the four
methods of the \linebreak \code{OptimisatioProblem} class; (a)
\code{solve_gradients(**kwargs)}, (b) \code{solve_bo(**kwargs)},
\linebreak (c) \code{build_region(**kwargs)}, (d)
\code{fit_local_surrogate(**kwargs)}. The user can create a custom
class that inherits the basic \code{OptimisatioProblem} and, then,
overwrite any of the four functions with custom ones. Suppose a user
wants to fit Neural Networks as local surrogate models
\(\tilde{d}_i\). The user should overwrite the
\code{fit_local_surrogate(**kwargs)} function with one that internally
trains a neural network. In the following snippet we illustrate that,
using the \code{neural_network.MLPRegressor} class of the
\pkg{scikit-learn} package.

\begin{Code}
---------------------------------- python ----------------------------------
class CustomOptim(OptimisationProblem):
    def __init__(self, **kwargs):
        super(CustomOptim, self).__init__(**kwargs)

@@

        # helper function
        def local_surrogate(theta, model_scikit):
            assert theta.ndim == 1
            theta = np.expand_dims(theta, 0)
            return float(model_scikit.predict(theta))

        # create local surrogate model as a function of theta
        def create_local_surrogate(model):
            return partial(local_surrogate, model_scikit=model)

@@

            # train Neural Network
            mlp = MLPRegressor(hidden_layer_sizes=(10,10), solver='adam')
            model = Pipeline([('linear', mlp)])
            model = model.fit(x, y)
            local_surrogates.append(create_local_surrogate(model))

        self.local_surrogates = local_surrogates
        self.state["local_surrogates"] = True
----------------------------------------------------------------------------
\end{Code}

In the same way, the user may replace each of the other three
functionalities. The only restriction that must be respected, concerns
the side-effects each method has at the \code{OptimisatioProblem}
class level. In the following four snippets we present the signature
of each method. We name the class-level variables that must be set
under the comment \code{\# side-effects}.

\begin{Code}
---------------------------------- python ----------------------------------
def solve_gradients(self, **kwargs):
  # custom solution procedure
  x = ...
  y = ...
  jac = ...
  hess_inv = ...

  # side-effects
  self.state["attempted"] = True
  if success:
    self.result = RomcOpimisationResult(x, y, jac, hess_inv)
    self.state["solved"] = True
    return True
  else:
    return False
----------------------------------------------------------------------------
def solve_bo(self, **kwargs):
  # custom procedure
  x = ...
  y = ...
  custom_surrogate = ...

  # side-effects
  self.state["attempted"] = True
  if success:
    self.result = RomcOpimisationResult(x, y)
    self.surrogate = custom_surrogate
    self.state["solved"] = True
    self.state["has_fit_surrogate"] = True
    return True
  else:
    return False
----------------------------------------------------------------------------
def build_region(self, **kwargs):
  # custom build_region method
  bounding_box: List[NDimBoudningBox] = ...
  success = True/False # whether region built correctly

  # side-effects
  self.eps_region = eps_region
  if success:
    # construct region
    self.regions = bounding_box
    self.state["region"] = True
    return True
  else:
    return False
----------------------------------------------------------------------------
def fit_local_surrogate(self, **kwargs):
  # custom local surrogates
  custom_surrogates = ...
  success = True/False # whether local surrogates fit correctly

  # side-effects
  if success:
    self.local_surrogate = local_surrogates
    self.state["local_surrogates"] = True
    return True
  else:
    return False
----------------------------------------------------------------------------    
\end{Code}
